\TitlePt

### 2016-03-19 conclusion.tex
Add citations to Tesseroids in the conclusion
Tweaks to last paragraph of conclusions

The \textit{Tesseroids} software is a collection of command-line
programs developed in the C programming language.
The programs calculate the gravitational potential and its first and second
derivatives of a tesseroid (spherical prism) model.
We implemented and improved upon an adaptive discretization algorithm to
guarantee the accuracy of the computations.
The adaptive discretization is controlled by a scalar called the distance-size
ratio ($D$).
Higher values of $D$ result in finner discretization and vice-versa.
Furthermore, we investigated the accuracy of the calculations as a function of
$D$.
Contrary to previous assumptions, our results showed that the first and second
derivatives require finner discretization than the gravitational potential to
achieve the same accuracy level.
The values of the distance-size ratio that yield a maximum error of 0.1\%
are $D = 1$ for the gravitational potential, $D = 1.5$ for the first
derivatives, and $D = 8$ for the second derivatives.
These values are included as defaults in version 1.2 of the \textit{Tesseroids}
software.

@@

In conclusion,
we have successfully applied the algorithms and software foundation developed
here to solve a geophysical inverse problem.
This application demonstrates that the same approach can be used to aid the
development of new inversion methods in the future.
In addition, both software packages were successful in gaining third-party
users.
\textit{Fatiando a Terra}, in particular, was able to gather other developers
to contribute source code to the software.
This will enable the continued growth of the project and is only possible
because the project is open-source.

>>>>

The \textit{Tesseroids} software is a collection of command-line
programs developed in the C programming language.
The programs calculate the gravitational potential and its first and second
derivatives of a tesseroid (spherical prism) model.
We implemented and improved upon an adaptive discretization algorithm to
guarantee the accuracy of the computations.
The adaptive discretization is controlled by a scalar called the distance-size
ratio ($D$).
Higher values of $D$ result in finner discretization and vice-versa.
Furthermore, we investigated the accuracy of the calculations as a function of
$D$.
Contrary to previous assumptions, our results showed that the first and second
derivatives require finner discretization than the gravitational potential to
achieve the same accuracy level.
The values of the distance-size ratio that yield a maximum error of 0.1\%
are $D = 1$ for the gravitational potential, $D = 1.5$ for the first
derivatives, and $D = 8$ for the second derivatives.
These values are included as defaults in version 1.2 of the software.
\textit{Tesseroids} has been used in published research by, for example,
\citet{braitenberg2011}, \citet{alvarez2012}, \citet{bouman2013},
\citet{bouman2013a}, \citet{mariani2013}, \citet{braitenberg2015}, and
\citet{fullea2015a}.

@@

In conclusion,
we have successfully applied the algorithms and software foundation developed
here to solve a geophysical inverse problem.
This application demonstrates that the same approach can be used to aid the
development of new inversion methods in the future.
In addition, both software packages were successful in gaining third-party
users and have been applied to solve real world scientific problems.
\textit{Fatiando a Terra}, in particular, was able to gather other developers
to contribute source code to the software, enabling the continued growth of the
project in the future.
We emphasize that this is only possible because the project is open-source and
freely available.
